% TF--PT weight transfer manuscript — Overleaf-ready
% Upload: main.tex, body.tex, and folder figures/ (copy from repo figures/)
\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{float}
\usepackage{caption}
\captionsetup{font=small,labelfont=bf}
\usepackage[hidelinks,unicode]{hyperref}
\usepackage{url}
\usepackage{microtype}

\graphicspath{{figures/}}

\title{Porting institutional deep-learning pickers to PyTorch and SeisBench: a practical guide to TensorFlow--PyTorch weight transfer (EQCCT case study)}
\author{C. Skevofilax \and A. Savvaidis \\[0.5em] \normalsize The University of Texas at Austin}
\date{\today}

\begin{document}
\maketitle

\noindent\textbf{Keywords:} seismic phase picking; deep learning; model portability; TensorFlow; PyTorch; SeisBench; EQCCT; weight transfer; reproducibility

\vspace{1em}

\begin{abstract}
Seismic research groups often train their own phase-picking models using whatever machine learning framework fits best into their existing workflow, and TensorFlow/Keras is still a popular choice. Meanwhile, much of the modern open-source seismology ecosystem has standardized on PyTorch. Tools like SeisBench, which are widely used in the community, are built entirely in PyTorch. Recent surveys show that PyTorch now dominates deep learning research, and many toolkits have adopted it to make their software easier to use and more accessible.

This creates a practical problem: models trained in TensorFlow cannot be added to platforms like SeisBench without first being converted to PyTorch. Without a reliable way to convert models between frameworks, research groups cannot easily share their work or integrate it into modern workflows, which limits both usability and long-term impact.

In this work, we present a practical, step-by-step workflow for converting transformer-based phase pickers, specifically EQCCT, from TensorFlow to PyTorch. We use our open-source implementation as a case study and describe the core challenges that determine whether conversion is scientifically and operationally trustworthy: weight-loading inconsistencies in Keras, ambiguity when mapping dense layers with square weight matrices, missing output branches in earlier model versions, and device-dependent numerical differences on GPU. We validate the converted model with a staged protocol that combines layer-wise weight and activation checks with end-to-end comparisons on real waveforms, including a SeisBench-scale benchmark on 100{,}000 windows from TXED and STEAD. In that benchmark, mean absolute error between TensorFlow and PyTorch probability traces is on the order of $10^{-9}$ on CPU and $10^{-7}$--$10^{-6}$ on GPU, with all windows remaining below $10^{-2}$ in worst-case pointwise discrepancy. The result is a reproducible guide for making non-PyTorch pickers compatible with PyTorch-centric tooling without retraining, and a template for reporting numerical parity in a form that supports deployment in persistent model-worker systems such as RAPID.
\end{abstract}

\input{body}

\end{document}
